---
title: "results"
author: "Raphaël Powis"
date: "2024-08-19"
output: html_document
---

#sample size

##% incomplete data
##incomplete days
```{r}
1-sum(tar_read(per_box_day)$duration)/sum(tar_read(per_box_day_tr0)$duration)
```

##incomplete phase
```{r}
per_box_phase <- tar_read(per_box_phase)
per_box_phase$breeding_attempt <- paste(per_box_phase$year,per_box_phase$box)
pr <- filter(per_box_phase,phase == "Provisioning")
length(unique(pr)$breeding_attempt) - length(unique(filter(pr,enough_prospect_data))$breeding_attempt)

pr <- filter(per_box_phase,phase == "Incubation")
length(unique(pr)$breeding_attempt) - length(unique(filter(pr,enough_prospect_data))$breeding_attempt)

pr <- filter(pr,phase == "Fledge")
length(unique(pr)$breeding_attempt) - length(unique(filter(pr,enough_prospect_data))$breeding_attempt)

```
##general descriptive results

```{r}
duration <- tar_read(duration)
sum((duration)$total_duration,na.rm = T)*24
sum(filter(duration, year(first_read) == 2023)$total_duration,na.rm = T)*24
sum(filter(duration, year(first_read) == 2022)$total_duration,na.rm = T)*24
visits <- tar_read(visits)
length(unique(visits$box))
nrow(filter(visits,age > 1))
nrow(filter(visits,age > 1 & year == 2023))
nrow(filter(visits,age > 1 & year == 2022))
length(unique(filter(visits,age > 1)$JID))
nrow(filter(visits,age > 1 & visitor_type == "P"))

pbd <- tar_read(per_box_day)
mean(pbd$prospect_visits)
sd(pbd$prospect_visits)
mean(pbd$n_visitors)
sd(pbd$n_visitors)

pbirdd <- tar_read(per_bird_day)
mean(pbirdd$prospect_visits)
sd(pbirdd$prospect_visits)

mean(filter(visits,distance < 1000)$distance,na.rm = T)
sd(filter(visits,distance < 1000)$distance,na.rm= T)
nrow(filter(visits,distance >= 1000))
```


# Individual characteristics of all prospectors

## all phases

```{r}
model <- tar_read(indiv_model)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
```

without thresholds

```{r}
model <- tar_read(indiv_model_tr0)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
testOutliers(simulationOutput1,type = "bootstrap")
```


## incubation


```{r}
model <- tar_read(indiv_model_incub)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
```

without thresholds

```{r}
model <- tar_read(indiv_model_incub_tr0)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
```

## provisioning


```{r}
model <- tar_read(indiv_model_prov)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
testDispersion(simulationOutput1)
```

without thresholds

```{r}
model <- tar_read(indiv_model_prov_tr0)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
testDispersion(simulationOutput1)
```


## post-fledgling


```{r}
model <- tar_read(indiv_model_pf)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
testDispersion(simulationOutput1)
```

without thresholds

```{r}
model <- tar_read(indiv_model_pf_tr0)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
testDispersion(simulationOutput1)
```

# trade-off parental activity-prospecting


```{r}
model <- tar_read(parental_model)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
```

without thresholds

```{r}
model <- tar_read(parental_model_tr0)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
```

# effect of prospecting on breeding success


```{r}
model <- tar_read(fitness_model)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
```


without thresholds
```{r}
model <- tar_read(fitness_model_tr0)
summary(model)
simulationOutput1 <- simulateResiduals(fittedModel = model, plot = T, seed = 1)
```

# effect of breeding failure on individual prospecting effort


```{r}
model <- tar_read(bird_failure_model)
summary(model)
plot(tar_read(bird_failure_sim))
print(tar_read(bird_failure_tukey))
plot(tar_read(fig_failure_bird))
print(tar_read(failure_outlier_test))
data <- tar_read(bird_failure_data)
failed <- filter(data,fledglings == 0)
success <- filter(data,fledglings > 0)
print(length(unique(paste(failed$year,failed$JID))))
print(length(unique(paste(success$year,success$JID))))
print(length(unique(failed$JID)))
print(length(unique(success$JID)))
```


without thresholds
```{r}
model <- tar_read(bird_failure_model_tr0)
summary(model)
plot(tar_read(bird_failure_sim_tr0))
```

# Box level

## phase comparison

```{r}
model <- tar_read(phase_comparison_model)
summary(model)
plot(tar_read(phase_comp_sim))
print(tar_read(phase_comp_tukey))
print(tar_read(phase_comp_fig))

```

without thresholds

```{r}
model <- tar_read(phase_comparison_model_tr0)
summary(model)
plot(tar_read(phase_comp_sim_tr0))
```


## day by day evolution


```{r}
model <- tar_read(day_day_model)
summary(model)
plot(tar_read(day_day_sim))
print(tar_read(day_day_plot))
plot(tar_read(day_day_plot))

```

without thresholds

```{r}
model <- tar_read(day_day_model_tr0)
summary(model)
plot(tar_read(day_day_sim_tr0))
```


##corelation between parental activity and median chick number

```{r}
print(tar_read(colin))
```


## effect of parental activity on nestbox attractivness


```{r}
model <- tar_read(parental_only_model)
summary(model)
plot(tar_read(parental_only_sim))
print(tar_read(parental_plot))

```

without thresholds

```{r}
model <- tar_read(parental_only_model_tr0)
summary(model)
plot(tar_read(parental_only_sim_tr0))

```

## effect of median chick number on nestbox attractivness


```{r}
model <- tar_read(chick_only_model)
summary(model)
plot(tar_read(chick_only_sim))
print(tar_read(chick_plot))

```

without thresholds

```{r}
model <- tar_read(chick_only_model_tr0)
summary(model)
plot(tar_read(chick_only_sim_tr0))

```

## parental activity and chick number in one combined model



```{r}
model <- tar_read(chick_parental_model)
summary(model)
plot(tar_read(chick_parental_sim))


```

without thresholds

```{r}
model <- tar_read(chick_parental_model_tr0)
summary(model)
plot(tar_read(chick_parental_sim_tr0))

```


## effect of breeding failure on nestbox attractivness

### all periods combined


```{r}
model <- tar_read(box_failure_model)
summary(model)
plot(tar_read(box_failure_sim))
data <- tar_read(box_failure_data)
failed <- filter(data,fledglings == 0)
success <- filter(data,fledglings > 0)
print(length(unique(paste(failed$year,failed$box))))
print(length(unique(paste(success$year,success$box))))
print(length(unique(failed$JID)))
print(length(unique(success$JID)))

```

without thresholds



```{r}
model <- tar_read(box_failure_model_tr0)
summary(model)
plot(tar_read(box_failure_sim_tr0))


```

### only pre-fledge




```{r}
model <- tar_read(box_failure_preFledge_model)
summary(model)
plot(tar_read(failure_preFledge_sim))
print(tar_read(failure_preFledge_tukey))

```

without thresholds

```{r}
model <- tar_read(box_failure_preFledge_model_tr0)
summary(model)
plot(tar_read(failure_preFledge_sim_tr0))
print(tar_read(failure_preFledge_tukey_tr0))

```

### only post-fledge




```{r}
model <- tar_read(box_failure_fledge_model)
summary(model)
plot(tar_read(failure_fledge_sim))
print(tar_read(failure_fledge_tukey))


```

without thresholds

```{r}
model <- tar_read(box_failure_fledge_model_tr0)
summary(model)
plot(tar_read(failure_fledge_sim_tr0))
print(tar_read(failure_fledge_tukey_tr0))

```












